---
title: "ITnewsheader articlelist"
date: "`r format(Sys.time(),'%Y/%m/%d %H:%M:%S')`"
output: 
  html_document:
    css: main.css
---

```{r setup,include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo=TRUE,include=TRUE,message=FALSE,warning=FALSE,error=FALSE,tidy=FALSE,cache=FALSE)
```

```{r read_script,include=FALSE}
library(Hmisc)
library(DT)

# render.Rは読み込まない（無限に循環してしまう）ので、render.Rは"./R"には置かない
walk(list.files("./R",pattern=".R$",recursive=TRUE,full.names=TRUE),source,encoding="UTF-8")
```

```{r get_data,include=FALSE}
ITmedia <- get_ITmedia_articlelist(USER_AGENT,SLEEP_TIME)
ITmedia_news <- map_dfr(ITMEDIA_YYMM,~possibly(get_ITmedia_news_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
ITmedia_pcuser <- map_dfr(ITMEDIA_YYMM,~possibly(get_ITmedia_pcuser_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
ITmedia_enterprise <- map_dfr(ITMEDIA_YYMM,~possibly(get_ITmedia_enterprise_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
ITmedia_mobile <- map_dfr(ITMEDIA_YYMM,~possibly(get_ITmedia_mobile_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
ITmedia_business <- map_dfr(ITMEDIA_YYMM,~possibly(get_ITmedia_business_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
atmarkit <- map_dfr(ITMEDIA_YYMM,~possibly(get_atmarkit_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
netlabo <- map_dfr(ITMEDIA_YYMM,~possibly(get_netlabo_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))

nikkei_xtech <- map_dfr(1:NIKKEI_XTECH_PAGES,~get_nikkei_xtech_articlelist(.x,USER_AGENT,SLEEP_TIME))

ascii <- map_dfr(ASCII_YYYYMM,~possibly(get_ascii_articlelist,NULL)("top",.x,USER_AGENT,SLEEP_TIME))
ascii_ai <- map_dfr(ASCII_YYYYMM,~possibly(get_ascii_articlelist,NULL)("ai",.x,USER_AGENT,SLEEP_TIME))
ascii_biz <- map_dfr(ASCII_YYYYMM,~possibly(get_ascii_articlelist,NULL)("biz",.x,USER_AGENT,SLEEP_TIME))
ascii_tech <- map_dfr(ASCII_YYYYMM,~possibly(get_ascii_articlelist,NULL)("tech",.x,USER_AGENT,SLEEP_TIME))
ascii_akiba <- map_dfr(ASCII_YYYYMM,~possibly(get_ascii_articlelist,NULL)("akiba",.x,USER_AGENT,SLEEP_TIME))

impress <- map_dfr(IMPRESS_YYYYMM,~possibly(get_impress_articlelist,NULL)("top",.x,USER_AGENT,SLEEP_TIME))
impress_internet <- map_dfr(IMPRESS_YYYYMM,~possibly(get_impress_articlelist,NULL)("internet",.x,USER_AGENT,SLEEP_TIME))
impress_pc <- map_dfr(IMPRESS_YYYYMM,~possibly(get_impress_articlelist,NULL)("pc",.x,USER_AGENT,SLEEP_TIME))
impress_akiba <- map_dfr(IMPRESS_YYYYMM,~possibly(get_impress_articlelist,NULL)("akiba-pc",.x,USER_AGENT,SLEEP_TIME))
impress_ktai <- map_dfr(IMPRESS_YYYYMM,~possibly(get_impress_articlelist,NULL)("k-tai",.x,USER_AGENT,SLEEP_TIME))
impress_cloud <- map_dfr(IMPRESS_YYYYMM,~possibly(get_impress_articlelist,NULL)("cloud",.x,USER_AGENT,SLEEP_TIME))
impress_hobby <- map_dfr(IMPRESS_YYYYMM,~possibly(get_impress_articlelist,NULL)("hobby",.x,USER_AGENT,SLEEP_TIME))

data <- Hmisc::llist(
  ITmedia,ITmedia_news,ITmedia_pcuser,ITmedia_enterprise,ITmedia_mobile,ITmedia_business,atmarkit,netlabo,
  nikkei_xtech,
  ascii,ascii_ai,ascii_biz,ascii_tech,ascii_akiba,
  impress,impress_internet,impress_pc,impress_akiba,impress_ktai,impress_cloud,impress_hobby
) %>% 
  map(~{
    .x %>% 
      mutate(date=as.character(date,format="%m/%d"))
  }) %>% 
  map(~make_table_for_report(.x,"DT"))
```

```{r DT_options,echo=FALSE}
DT_options <- list(
  pageLength=1000,
  scrollX=TRUE,
  ordering=FALSE,
  select=FALSE,
  columnDefs=list(list(width="6rem",targets=0))
)
```

## {.tabset}

### ITmedia

`r nrow(data$ITmedia)` entries (`r str_glue("{last(data$ITmedia$date)} - {first(data$ITmedia$date)}")`)

```{r ITmedia,echo=FALSE}
DT::datatable(data$ITmedia,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### ITmedia_news

`r nrow(data$ITmedia_news)` entries (`r str_glue("{last(data$ITmedia_news$date)} - {first(data$ITmedia_news$date)}")`)

```{r ITmedia_news,echo=FALSE}
DT::datatable(data$ITmedia_news,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### ITmedia_pcuser

`r nrow(data$ITmedia_pcuser)` entries (`r str_glue("{last(data$ITmedia_pcuser$date)} - {first(data$ITmedia_pcuser$date)}")`)

```{r ITmedia_pcuser,echo=FALSE}
DT::datatable(data$ITmedia_pcuser,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### ITmedia_enterprise

`r nrow(data$ITmedia_enterprise)` entries (`r str_glue("{last(data$ITmedia_enterprise$date)} - {first(data$ITmedia_enterprise$date)}")`)

```{r ITmedia_enterprise,echo=FALSE}
DT::datatable(data$ITmedia_enterprise,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### ITmedia_mobile

`r nrow(data$ITmedia_mobile)` entries (`r str_glue("{last(data$ITmedia_mobile$date)} - {first(data$ITmedia_mobile$date)}")`)

```{r ITmedia_mobile,echo=FALSE}
DT::datatable(data$ITmedia_mobile,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### ITmedia_business

`r nrow(data$ITmedia_business)` entries (`r str_glue("{last(data$ITmedia_business$date)} - {first(data$ITmedia_business$date)}")`)

```{r ITmedia_business,echo=FALSE}
DT::datatable(data$ITmedia_business,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### atmarkit

`r nrow(data$atmarkit)` entries (`r str_glue("{last(data$atmarkit$date)} - {first(data$atmarkit$date)}")`)

```{r atmarkit,echo=FALSE}
DT::datatable(data$atmarkit,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### netlabo

`r nrow(data$netlabo)` entries (`r str_glue("{last(data$netlabo$date)} - {first(data$netlabo$date)}")`)

```{r netlabo,echo=FALSE}
DT::datatable(data$netlabo,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### nikkei_xtech

`r nrow(data$nikkei_xtech)` entries (`r str_glue("{last(data$nikkei_xtech$date)} - {first(data$nikkei_xtech$date)}")`)

```{r nikkei_xtech,echo=FALSE}
DT::datatable(data$nikkei_xtech,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### ascii

`r nrow(data$ascii)` entries (`r str_glue("{last(data$ascii$date)} - {first(data$ascii$date)}")`)

```{r ascii,echo=FALSE}
DT::datatable(data$ascii,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### ascii_ai

`r nrow(data$ascii_ai)` entries (`r str_glue("{last(data$ascii_ai$date)} - {first(data$ascii_ai$date)}")`)

```{r ascii_ai,echo=FALSE}
DT::datatable(data$ascii_ai,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### ascii_biz

`r nrow(data$ascii_biz)` entries (`r str_glue("{last(data$ascii_biz$date)} - {first(data$ascii_biz$date)}")`)

```{r ascii_biz,echo=FALSE}
DT::datatable(data$ascii_biz,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### ascii_tech

`r nrow(data$ascii_tech)` entries (`r str_glue("{last(data$ascii_tech$date)} - {first(data$ascii_tech$date)}")`)

```{r ascii_tech,echo=FALSE}
DT::datatable(data$ascii_tech,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### ascii_akiba

`r nrow(data$ascii_akiba)` entries (`r str_glue("{last(data$ascii_akiba$date)} - {first(data$ascii_akiba$date)}")`)

```{r ascii_akiba,echo=FALSE}
DT::datatable(data$ascii_akiba,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### impress

`r nrow(data$impress)` entries (`r str_glue("{last(data$impress$date)} - {first(data$impress$date)}")`)

```{r impress,echo=FALSE}
DT::datatable(data$impress,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### impress_internet

`r nrow(data$impress_internet)` entries (`r str_glue("{last(data$impress_internet$date)} - {first(data$impress_internet$date)}")`)

```{r impress_internet,echo=FALSE}
DT::datatable(data$impress_internet,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### impress_pc

`r nrow(data$impress_pc)` entries (`r str_glue("{last(data$impress_pc$date)} - {first(data$impress_pc$date)}")`)

```{r impress_pc,echo=FALSE}
DT::datatable(data$impress_pc,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### impress_akiba

`r nrow(data$impress_akiba)` entries (`r str_glue("{last(data$impress_akiba$date)} - {first(data$impress_akiba$date)}")`)

```{r impress_akiba,echo=FALSE}
DT::datatable(data$impress_akiba,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### impress_ktai

`r nrow(data$impress_ktai)` entries (`r str_glue("{last(data$impress_ktai$date)} - {first(data$impress_ktai$date)}")`)

```{r impress_ktai,echo=FALSE}
DT::datatable(data$impress_ktai,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### impress_cloud

`r nrow(data$impress_cloud)` entries (`r str_glue("{last(data$impress_cloud$date)} - {first(data$impress_cloud$date)}")`)

```{r impress_cloud,echo=FALSE}
DT::datatable(data$impress_cloud,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```

### impress_hobby

`r nrow(data$impress_hobby)` entries (`r str_glue("{last(data$impress_hobby$date)} - {first(data$impress_hobby$date)}")`)

```{r impress_hobby,echo=FALSE}
DT::datatable(data$impress_hobby,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,options=DT_options)
```
