---
title: "ITnewsheader articlelist"
date: "`r format(Sys.time(),'%Y/%m/%d %H:%M:%S')`"
output: 
  html_document:
    css: main.css
---

```{r setup,include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo=TRUE,include=TRUE,message=FALSE,warning=FALSE,error=FALSE,tidy=FALSE,cache=FALSE)
```


```{r,include=FALSE}
walk(list.files(".",pattern=".R$",recursive=TRUE,full.names=TRUE),source,encoding="UTF-8")
```

```{r,include=FALSE}
ITmedia <- get_ITmedia_articlelist(USER_AGENT,SLEEP_TIME)
ITmedia_news <- map_dfr(YYMM,~possibly(get_ITmedia_news_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
ITmedia_pcuser <- map_dfr(YYMM,~possibly(get_ITmedia_pcuser_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
ITmedia_enterprise <- map_dfr(YYMM,~possibly(get_ITmedia_enterprise_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
ITmedia_mobile <- map_dfr(YYMM,~possibly(get_ITmedia_mobile_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
ITmedia_business <- map_dfr(YYMM,~possibly(get_ITmedia_business_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
atmarkit <- map_dfr(YYMM,~possibly(get_atmarkit_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))
netlabo <- map_dfr(YYMM,~possibly(get_netlabo_articlelist,NULL)(.x,USER_AGENT,SLEEP_TIME))

nikkei_xtech <- map_dfr(1:NIKKEI_XTECH_PAGES,~get_nikkei_xtech_articlelist(.x,USER_AGENT,SLEEP_TIME))

ascii <- map_dfr(YYYYMM,~possibly(get_ascii_articlelist,NULL)("top",.x,USER_AGENT,SLEEP_TIME))
ascii_ai <- map_dfr(YYYYMM,~possibly(get_ascii_articlelist,NULL)("ai",.x,USER_AGENT,SLEEP_TIME))
ascii_biz <- map_dfr(YYYYMM,~possibly(get_ascii_articlelist,NULL)("biz",.x,USER_AGENT,SLEEP_TIME))
ascii_tech <- map_dfr(YYYYMM,~possibly(get_ascii_articlelist,NULL)("tech",.x,USER_AGENT,SLEEP_TIME))
ascii_akiba <- map_dfr(YYYYMM,~possibly(get_ascii_articlelist,NULL)("akiba",.x,USER_AGENT,SLEEP_TIME))

impress <- map_dfr(YYYYMM,~possibly(get_impress_articlelist,NULL)("top",.x,USER_AGENT,SLEEP_TIME))
impress_internet <- map_dfr(YYYYMM,~possibly(get_impress_articlelist,NULL)("internet",.x,USER_AGENT,SLEEP_TIME))
impress_pc <- map_dfr(YYYYMM,~possibly(get_impress_articlelist,NULL)("pc",.x,USER_AGENT,SLEEP_TIME))
impress_akiba <- map_dfr(YYYYMM,~possibly(get_impress_articlelist,NULL)("akiba-pc",.x,USER_AGENT,SLEEP_TIME))
impress_ktai <- map_dfr(YYYYMM,~possibly(get_impress_articlelist,NULL)("k-tai",.x,USER_AGENT,SLEEP_TIME))
impress_cloud <- map_dfr(YYYYMM,~possibly(get_impress_articlelist,NULL)("cloud",.x,USER_AGENT,SLEEP_TIME))
impress_hobby <- map_dfr(YYYYMM,~possibly(get_impress_articlelist,NULL)("hobby",.x,USER_AGENT,SLEEP_TIME))

data <- Hmisc::llist(
  ITmedia,ITmedia_news,ITmedia_pcuser,ITmedia_enterprise,ITmedia_mobile,ITmedia_business,atmarkit,netlabo,
  nikkei_xtech,
  ascii,ascii_ai,ascii_biz,ascii_tech,ascii_akiba,
  impress,impress_internet,impress_pc,impress_akiba,impress_ktai,impress_cloud,impress_hobby
) %>% 
  map(~make_table_for_report(.x,"DT"))
```

## {.tabset}

### ITmedia

`r nrow(data$ITmedia)` entries

```{r,echo=FALSE}
DT::datatable(data$ITmedia,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### ITmedia_news

`r nrow(data$ITmedia_news)` entries

```{r,echo=FALSE}
DT::datatable(data$ITmedia_news,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### ITmedia_pcuser

`r nrow(data$ITmedia_pcuser)` entries

```{r,echo=FALSE}
DT::datatable(data$ITmedia_pcuser,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### ITmedia_enterprise

`r nrow(data$ITmedia_enterprise)` entries

```{r,echo=FALSE}
DT::datatable(data$ITmedia_enterprise,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### ITmedia_mobile

`r nrow(data$ITmedia_mobile)` entries

```{r,echo=FALSE}
DT::datatable(data$ITmedia_mobile,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### ITmedia_business

`r nrow(data$ITmedia_business)` entries

```{r,echo=FALSE}
DT::datatable(data$ITmedia_business,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### atmarkit

`r nrow(data$atmarkit)` entries

```{r,echo=FALSE}
DT::datatable(data$atmarkit,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### netlabo

`r nrow(data$netlabo)` entries

```{r,echo=FALSE}
DT::datatable(data$netlabo,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### nikkei_xtech

`r nrow(data$nikkei_xtech)` entries

```{r,echo=FALSE}
DT::datatable(data$nikkei_xtech,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### ascii

`r nrow(data$ascii)` entries

```{r,echo=FALSE}
DT::datatable(data$ascii,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### ascii_ai

`r nrow(data$ascii_ai)` entries

```{r,echo=FALSE}
DT::datatable(data$ascii_ai,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### ascii_biz

`r nrow(data$ascii_biz)` entries

```{r,echo=FALSE}
DT::datatable(data$ascii_biz,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### ascii_tech

`r nrow(data$ascii_tech)` entries

```{r,echo=FALSE}
DT::datatable(data$ascii_tech,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### ascii_akiba

`r nrow(data$ascii_akiba)` entries

```{r,echo=FALSE}
DT::datatable(data$ascii_akiba,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### impress

`r nrow(data$impress)` entries

```{r,echo=FALSE}
DT::datatable(data$impress,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### impress_internet

`r nrow(data$impress_internet)` entries

```{r,echo=FALSE}
DT::datatable(data$impress_internet,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### impress_pc

`r nrow(data$impress_pc)` entries

```{r,echo=FALSE}
DT::datatable(data$impress_pc,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### impress_akiba

`r nrow(data$impress_akiba)` entries

```{r,echo=FALSE}
DT::datatable(data$impress_akiba,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### impress_ktai

`r nrow(data$impress_ktai)` entries

```{r,echo=FALSE}
DT::datatable(data$impress_ktai,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### impress_cloud

`r nrow(data$impress_cloud)` entries

```{r,echo=FALSE}
DT::datatable(data$impress_cloud,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```

### impress_hobby

`r nrow(data$impress_hobby)` entries

```{r,echo=FALSE}
DT::datatable(data$impress_hobby,class="nowrap",colnames="",rownames=FALSE,escape=FALSE,
              options=list(pageLength=1000,scrollX=TRUE))
```
